EE454 Project 1 Report

### 2015-09-23 p1/report/latex/draft.tex
added sections in project summary

>>>>

\subsection{Purpose}
The purpose of this project was to implement a pre-trained convolutional neural network (CNN) using MATLAB.  The CNN is composed of layers - each layer performs an operation on a set of input matrices and produces a corresponding output matrix.  When these layers are composed together, they produce a network; the input of this network is an image, and the output of this network is a vector of classification probabilities.

\subsection{Operations}

\subsubsection{Image Normalization}
